Considerations for the Next Iteration of the DOE Fast Forward Storage and IO Project

### 2014-02-25 paper.tex
update for invalid cite text

The \DDT project created a simplistic model for a metadata service that has
different features that is described below and has been published about
previously~\cite{lofstead:2011:txn-metadata}. Some of the major differences
include the following. First, \DDTns's metadata service has a way to get a list
of the ojbjects in the metadata service. While it does not address having a
file equivalence like the container concept, it does introduce a way to figure
out what is available. Stored along with this object description is a list of
the global dimensions for array objects. One observtion made as part of
creating this service is that this is insufficient for many engineering codes
that use non-regular meshes. Second, for each object, a list of the equivalent
to shards are kept with a link back to the master object and the offset and
size for each dimension for that shard. This approach is not scalable because
of the explosion in the process count. Using a striping approach like IOD does
is superior. Third, there is no mapping to another layer with different object
layout and counts.

>>>>

The \DDT project created a simplistic model for a metadata service that has
different features that is described below and has been published about
previously~\cite{lofstead:2012:txn-metadata}. Some of the major differences
include the following. First, \DDTns's metadata service has a way to get a list
of the ojbjects in the metadata service. While it does not address having a
file equivalence like the container concept, it does introduce a way to figure
out what is available. Stored along with this object description is a list of
the global dimensions for array objects. One observtion made as part of
creating this service is that this is insufficient for many engineering codes
that use non-regular meshes. Second, for each object, a list of the equivalent
to shards are kept with a link back to the master object and the offset and
size for each dimension for that shard. This approach is not scalable because
of the explosion in the process count. Using a striping approach like IOD does
is superior. Third, there is no mapping to another layer with different object
layout and counts.
